# Introduction

This is a book created from markdown and executable code.

See @knuth84 for additional discussion of literate programming.

```{r}
1 + 1
```

Examples from https://github.com/hadley/r4ds/blob/main/intro.qmd


You can install the complete tidyverse with a single line of code:

```{r}
#| eval: false

install.packages("tidyverse")
```

On your computer, type that line of code in the console, and then press enter to run it.
R will download the packages from CRAN and install them on your computer.

## Running R code

The previous section showed you several examples of running R code.
The code in the book looks like this:

```{r}
#| eval: true
1 + 2
```

If you run the same code in your local console, it will look like this:

```         
> 1 + 2
[1] 3
```

There are two main differences.
In your console, you type after the `>`, called the **prompt**; we don't show the prompt in the book.
In the book, the output is commented out with `#>`; in your console, it appears directly after your code.
These two differences mean that if you're working with an electronic version of the book, you can easily copy code out of the book and paste it into the console.

Throughout the book, we use a consistent set of conventions to refer to code:

-   Functions are displayed in a code font and followed by parentheses, like `sum()` or `mean()`.

-   Other R objects (such as data or function arguments) are in a code font, without parentheses, like `flights` or `x`.

-   Sometimes, to make it clear which package an object comes from, we'll use the package name followed by two colons, like `dplyr::mutate()` or `nycflights13::flights`.
    This is also valid R code.